Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
ref to Haskell Report.
reference fix.

Haskell has a very strong type system, which ensures that most type errors are
detected at compile time rather than runtime.  Thanks to this, we assume that
programs written in Haskell have less bugs than programs written in programming
languages that do not provide such a strong type system.

@@

The word ``behavior'' is associated with actions.
Since pure functions of Haskell are static,
this word might be improper for Haskell.
However, to avoid to define a new terminology,
we use ``behavior'' in this paper.

\begin{quote}
    @kazu: We e.g. say ill-behaved Monoid instance.  So is
    ``behavior'' really a bad word?  But I agree that some people in
    the community might associated it with something imperative.

    One might also argue that ``should'' is not very mathematical, but
    it is common language when we talk about mathematics.  E.g. Brent
    Yorgey uses ``should'' a lot in the Typeclassopedia (e.g. ``\ldots
    {\tt Alternative} should satisfy the monoid laws\ldots'')
\end{quote}

>>>>

Haskell~\cite{haskell} has a very strong type system, which ensures that most type errors are
detected at compile time rather than runtime.  Thanks to this, we assume that
programs written in Haskell have less bugs than programs written in programming
languages that do not provide such a strong type system.

@@

The word ``behavior'' is associated with imperative actions.
Since pure functions of Haskell are static,
this word might be improper for Haskell.
However, this word is already used in Haskell community~\cite{typeclassopedia}.
So, we use ``behavior'' instead of defining a new terminology in this paper.

%% \begin{quote}
%%     @kazu: We e.g. say ill-behaved Monoid instance.  So is
%%     ``behavior'' really a bad word?  But I agree that some people in
%%     the community might associated it with something imperative.

%%     One might also argue that ``should'' is not very mathematical, but
%%     it is common language when we talk about mathematics.  E.g. Brent
%%     Yorgey uses ``should'' a lot in the Typeclassopedia (e.g. ``\ldots
%%     {\tt Alternative} should satisfy the monoid laws\ldots'')
%% \end{quote}
